Flowchart of Current Algorithm

### 2009-02-05 docs/flowchart/flowchart.tex
added note about moving correct base to Algorithm Updates Section
after react_state, set (rho h)_0 = Avg(rho h) in plane-parallel and (rho h)_0 = (rho h)_0 - Avg[(rho h)_0 - (rho h)] in spherical.
React Base no longer is called

rhoh_1 and rhoh_2 don't exist anymore.  Advect Base Enthalpy advances (rho h)^n to (rho h)^{n+1}

All of this is documented in the flowchart

\item We discuss spherical geometries, in paricular:
\begin{itemize}
\item We are still working out the fill, average, and interpolate stencils.
\item We are working on {\bf Advect Base}, {\bf React Base}, and 
{\bf Correct Base} details.
\item We are working on $\etarho$ details.
\item We compute the full state temperature on cell-centers after the 
advection-diffusion step using $T=T(\rho,X_k,p_0)$ by setting 
{\tt use\_tfromp = TRUE} rather than using $T=T(\rho,h,X_k)$.
\item We have changed the discretization of $\Ub\cdot\nabla p_0$ in the enthalpy
update to $\nabla\cdot(\Ub p_0) - p_0\nabla\cdot\Ub$.
\end{itemize}

@@

\item We have added the flag, {\tt full\_rhoh0\_evolution}, which defaults to 
{\tt TRUE} (note that we do not have a {\bf Correct Base} or 
{\bf Diffuse Base} for enthalpy).  When {\tt FALSE}, we do not call {\bf React Base},
but instead set $(\rho h)_0 = \overline{(\rho h)^n}$ before {\bf Advect Base}.

@@

@@

\item After {\bf React State}, should we set $(\rho h)_0 = {\rm{\bf Avg}}(\rho h)$ in 
plane-parallel and $(\rho h)_0 = (\rho h)_0 - {\rm{\bf Avg}}[(\rho h)_0 - (\rho h)]$ 
in spherical?  This can currently be done by making {\tt full\_rhoh0\_evolution = FALSE}.
This means that {\bf React Base} no longer has to exist, and the intermediate states, 
$(\rho h)_0^{(1)}$ and $(\rho h)_0^{(2)}$, no longer have to exist.  
{\bf Advect Base Enthalpy} will advance $(\rho h)_0^n \rightarrow (\rho h)_0^{n+1}$ 
directly.  This also means we don't have to deal with $\eta_{\rho h}$ or a 
{\bf Diffuse Base}.

@@

& \text{React Base} & & \text{Advect Base} & & \text{Correct Base} & & \text{React Base} & \\
\rho_0^n & & & \longrightarrow & \rho_0^{(2a)} & \longrightarrow & & & \rho_0^{n+1} \\
(\rho h)_0^n & \longrightarrow & (\rho h)_0^{(1)} & \longrightarrow & & & (\rho h)_0^{(2)} & \longrightarrow & (\rho h)_0^{n+1} \\
p_0^n & & & \longrightarrow & & & & & p_0^{n+1} \\

@@

\item {\bf React Base}$[(\rho h)_0^{\inp},\overline{(\rho\Hnuc)^{\inp}},\overline{(\rho\Hext)^{\inp}}] \rightarrow [(\rho h)_0^{\outp}]$\\
is the process by which we update the base state enthalpy through $\dt/2$ in time using
\begin{equation}
\frac{\partial(\rho h)_0}{\partial t} = \overline{(\rho\Hnuc)^{\inp}} + \overline{(\rho\Hext)^{\inp}}\enskip ,
\end{equation}
discretized as
\begin{equation}
(\rho h)_{0,j}^{\outp} = (\rho h)_{0,j}^{\inp} + \frac{\dt}{2}\overline{(\rho\Hnuc)_{j}^{\inp}} + \frac{\dt}{2}\overline{(\rho\Hext)_{j}^{\inp}} \enskip .
\end{equation}

@@

\item {\bf React State}$[\rho^n, (\rho h)^n, X_k^n, T^n, (\rho\Hext)^n]
                   \rightarrow$ $[ \rho^{(1)}, (\rho h)^{(1)}, X_k^{(1)}, T^{(1)},
                                  (\rho \omegadot_k)^{(1)}, (\rho \Hnuc)^{(1)} ].$

\item {\bf if} ~ {\tt full\_rhoh0\_evolution = T} ~ {\bf then}

~~~ {\bf React Base}$[(\rho h)_0^n,\overline{(\rho \Hnuc)^{(1)}},\overline{(\rho\Hext)^n}] \rightarrow [(\rho h)_0^{(1)}]$ \\
{\bf else}

~~~ $(\rho h)_0^{(1)} = \overline{(\rho h)^{(1)}}$ in plane-parallel

~~~ $(\rho h)_0^{(1)} = (\rho h)_0^{n} - {\rm{\bf Avg}}\left[(\rho h)_0^{n} - (\rho h)^{(1)}\right] $ in spherical. \\
{\bf end if}
\item Define
\begin{eqnarray}
\gammabar^{(1)}        &=& {\rm{\bf Avg}} \left[ \Gamma_1\left(\rho^{(1)}, p_0^{n}, X_k^{(1)}\right) \right] \enskip , \\
 {\beta   }_0^{(1)}    &=& \beta   \left(\rho_0^{n}, p_0^{n}, \gammabar^{(1)}\right) \enskip .
\end{eqnarray}
Here $\beta_0$ is computed as described in paper~III, Appendix C.

@@

\item {\bf Advect Base Enthalpy}$[(\rho h)_0^{(1)}, w_0^{\nph,\star}, \psi^{\nph,\star}]$ 
$\rightarrow [(\rho h)_0^{(2),\star}]$.

@@

\begin{equation}
(\rho h)^{(1),\nph,\star} = 
(\rho h)^{'(1),\nph,\star} + \frac{(\rho h)_0^n + (\rho h)_0^{(2),\star}}{2}
\enskip .
\end{equation}
  In plane-parallel, we use 4th-order spatial averaging to compute $(\rho h)_0$
  on radial faces.  In spherical, we first map $h_0 \equiv (\rho h)_0/\rho_0$ 
  and $\rho_0$ to Cartesian cell-centers using the mapping in Section 
  \ref{Sec:1D Cell-Centered to Cartesian Cell-Centered}, use 2nd-order spatial 
  averaging to compute $h_0$ and $\rho_0$ on all faces, and then multiply these 
  terms to get $(\rho h)_0$ on all faces.

@@

\item {\bf Advect Base Enthalpy}$[(\rho h)_0^{(1)}, w_0^{\nph}, \psi^{\nph}]$ 
$\rightarrow [(\rho h)_0^{(2)}]$.

@@

  \item Compute the enthalpy edge state, $(\rho h)^{(1),\nph}$, for
    the conservative update of $(\rho h)$. Here we predict $(\rho h)'$
    to the edges to obtain $(\rho h)^{'(1),\nph}$, 
    using a second-order Taylor expansion in space and
    time, as described in paper II, Appendix A, using $\Vb =
    \uadvtwo+w_0^{\nph} \er$.  Again, we do not include the reaction
    terms in the enthalpy prediction since we accounted for them
    already in {\bf React State}. We use the base state enthalpy,
    $(\rho h)_0$, to convert these to edge states for $(\rho h)$,
\begin{equation}
(\rho h)^{(1),\nph} = 
(\rho h)^{'(1),\nph} + \frac{(\rho h)_0^n + (\rho h)_0^{(2)}}{2} \enskip .
\end{equation}
  In plane-parallel, we use 4th-order spatial averaging to compute $(\rho h)_0$
  on radial faces.  In spherical, we first map $h_0 \equiv (\rho h)_0/\rho_0$ 
  and $\rho_0$ to Cartesian cell-centers using the mapping in Section 
  \ref{Sec:1D Cell-Centered to Cartesian Cell-Centered}, use 2nd-order spatial 
  averaging to compute $h_0$ and $\rho_0$ on all faces, and then multiply these 
  terms to get $(\rho h)_0$ on all faces.

@@

\item {\bf React Base}$[(\rho h)_0^{(2)},\overline{(\rho \Hnuc)^{(2)}},\overline{(\rho\Hext)^{(2)}}] \rightarrow [(\rho h)_0^{n+1}]$

>>>>

\item We discuss spherical geometries, in paricular:
\begin{itemize}
\item We are still working out the fill, average, and interpolate stencils.
\item We are working on {\bf Advect Base} and {\bf Correct Base} details.
\item We are working on $\etarho$ details.
\item We compute the full state temperature on cell-centers after the 
advection-diffusion step using $T=T(\rho,X_k,p_0)$ by setting 
{\tt use\_tfromp = TRUE} rather than using $T=T(\rho,h,X_k)$.
\item We have changed the discretization of $\Ub\cdot\nabla p_0$ in the enthalpy
update to $\nabla\cdot(\Ub p_0) - p_0\nabla\cdot\Ub$.
\end{itemize}

@@

@@

\item In {\bf Step 4} and {\bf Step 8}, we moved {\bf Correct Base} so it
occurs immediately before {\bf Advect Base Pressure}.  Since the full
enthalpy advance ``feels'' the effects of the time-centered $\etarho$, we should
rely on a $\rho_0^{n+1}$ that also feels the effects.

\item After {\bf React State}, we set $(\rho h)_0 = {\rm{\bf Avg}}(\rho h)$ in 
plane-parallel and $(\rho h)_0 = (\rho h)_0 - {\rm{\bf Avg}}[(\rho h)_0 - (\rho h)]$ 
in spherical.  This means that {\bf React Base} no longer exists, and the intermediate states, 
$(\rho h)_0^{(1)}$ and $(\rho h)_0^{(2)}$, no longer have to exist.  
{\bf Advect Base Enthalpy} will advance $(\rho h)_0^n \rightarrow (\rho h)_0^{n+1}$ 
directly.  This also means we don't have to deal with $\eta_{\rho h}$ or a 
{\bf Diffuse Base}.

@@

@@

\left.\begin{array}{ccccccc}
& \text{Advect Base} & & \text{Correct Base} & \\
\rho_0^n & \longrightarrow & \rho_0^{(2a)} & \longrightarrow & \rho_0^{n+1} \\
(\rho h)_0^n & \longrightarrow & & & (\rho h)_0^{n+1} \\
p_0^n & \longrightarrow & & & p_0^{n+1} \\

@@

@@

\item {\bf React State}$[\rho^n, (\rho h)^n, X_k^n, T^n, (\rho\Hext)^n]
                   \rightarrow$ $[ \rho^{(1)}, (\rho h)^{(1)}, X_k^{(1)}, T^{(1)},
                                  (\rho \omegadot_k)^{(1)}, (\rho \Hnuc)^{(1)} ].$
\item
\begin{description}

\item[plane-parallel:] Set $(\rho h)_0^{n} = \overline{(\rho h)^{(1)}}$.

\item[spherical:] Set $(\rho h)_0^{n} = (\rho h)_0^{n} - {\rm{\bf Avg}}\left[(\rho h)_0^{n} - (\rho h)^{(1)}\right]$.

\item Define
\begin{eqnarray}
\gammabar^{(1)}        &=& {\rm{\bf Avg}} \left[ \Gamma_1\left(\rho^{(1)}, p_0^{n}, X_k^{(1)}\right) \right] \enskip , \\
 {\beta   }_0^{(1)}    &=& \beta   \left(\rho_0^{n}, p_0^{n}, \gammabar^{(1)}\right) \enskip .
\end{eqnarray}
Here $\beta_0$ is computed as described in paper~III, Appendix C.

@@

\item {\bf Advect Base Enthalpy}$[(\rho h)_0^{n}, w_0^{\nph,\star}, \psi^{\nph,\star}]$ 
$\rightarrow [(\rho h)_0^{n+1,\star}]$.

@@

\begin{equation}
(\rho h)^{(1),\nph,\star} = 
(\rho h)^{'(1),\nph,\star} + \frac{(\rho h)_0^n + (\rho h)_0^{n+1,\star}}{2}
\enskip .
\end{equation}
  In plane-parallel, we use 4th-order spatial averaging to compute $(\rho h)_0$
  on radial faces.  In spherical, we first map $h_0 \equiv (\rho h)_0/\rho_0$ 
  and $\rho_0$ to Cartesian cell-centers using the mapping in Section 
  \ref{Sec:1D Cell-Centered to Cartesian Cell-Centered}, use 2nd-order spatial 
  averaging to compute $h_0$ and $\rho_0$ on all faces, and then multiply these 
  terms to get $(\rho h)_0$ on all faces.

@@

\item {\bf Advect Base Enthalpy}$[(\rho h)_0^{n}, w_0^{\nph}, \psi^{\nph}]$ 
$\rightarrow [(\rho h)_0^{n+1}]$.

@@

  \item Compute the enthalpy edge state, $(\rho h)^{(1),\nph}$, for
    the conservative update of $(\rho h)$. Here we predict $(\rho h)'$
    to the edges to obtain $(\rho h)^{'(1),\nph}$, 
    using a second-order Taylor expansion in space and
    time, as described in paper II, Appendix A, using $\Vb =
    \uadvtwo+w_0^{\nph} \er$.  Again, we do not include the reaction
    terms in the enthalpy prediction since we accounted for them
    already in {\bf React State}. We use the base state enthalpy,
    $(\rho h)_0$, to convert these to edge states for $(\rho h)$,
\begin{equation}
(\rho h)^{(1),\nph} = 
(\rho h)^{'(1),\nph} + \frac{(\rho h)_0^n + (\rho h)_0^{n+1}}{2} \enskip .
\end{equation}
  In plane-parallel, we use 4th-order spatial averaging to compute $(\rho h)_0$
  on radial faces.  In spherical, we first map $h_0 \equiv (\rho h)_0/\rho_0$ 
  and $\rho_0$ to Cartesian cell-centers using the mapping in Section 
  \ref{Sec:1D Cell-Centered to Cartesian Cell-Centered}, use 2nd-order spatial 
  averaging to compute $h_0$ and $\rho_0$ on all faces, and then multiply these 
  terms to get $(\rho h)_0$ on all faces.

@@
